Czech parliament meeting recordings as ASR training data

### 2020-05-04 2020-tsd-brno-svolocz/svolocz-anonymous.tex
svolocz: add cross-corpora ASR

\section{Introduction}

@@

I have trained a standard DeepSpeech\cite{hannun2014deep} model on the 1058
hours with training :
development : test ratio of 48 : 1 : 1; batch size 50; learning rate 0.0001; dropout
rate 0.2. The training took 12 epochs to reach optimal dev fit and the final
word error rate on testing data from the corpus itself is 8.40\%.

@@

@@

I have presented a new corpus of spoken Czech suitable for training speech
recognition systems based on data in the public domain. The corpus size exceed
by an order the size of other freely available such corpora. A speech
recognition system with competitive performance was made to show the fitness
of the dataset to the purpose.

>>>>

\section{Introduction}
\label{sec:intro}

@@

I have trained a standard DeepSpeech\cite{hannun2014deep} model on the 1058
hours with training :
development : test ratio of 18 : 1 : 1; batch size 50; learning rate 0.0001; dropout
rate 0.2. The training took 12 epochs to reach optimal dev fit and the final
word error rate on testing data from the corpus itself is 8.40\%.

@@

I have also tried training a speech recognition system with other datasets and
the combination of them all. Of the datasets listed in
section~\ref{sec:intro}, only Vystadial, Otázky Václava Moravce (ovm) and the
corpus of Karel Makoň (makon) proved useful without much effort.

Apart from them, I used the publicly not available corpora of Charles University
Corpus of Financial News (CUCFN, 65 hours)\cite{byrne1999large}, the Balanced
corpus of informal spoken Czech (Oral2013, 293 hours)\cite{oral2013} and the
spoken Bible (100 hours) available with no license terms from {\em
poslouchamebibli.cz}. Table~\ref{tab:csasr:results} shows the speech recognition
results for each corpus on test data from itself and on a common test set from
all the corpora.

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
source    & WER on self & WER on all \\
\hline
bible     & 9.20\%  & 94.7\% \\
cucfgn    & 31.6\%  & 72.8\% \\
makon     & 30.4\%  & 77.3\% \\
oral2013  & 78.4\%  & 60.7\% \\
ovm       & 21.6\%  & 72.9\% \\
\textbf{parliament}
          & 8.74\%  & \textbf{39.7\%} \\
vystadial & 51.0\%  & 74.0\% \\
\hline
all       & 28.4\%  & 28.4\% \\
\hline
\end{tabular}
\caption{Word error rate of speech recognition on the individual corpora and on
their concatenation.}\label{tab:csasr:results}
\end{center}
\end{table}

All speech recognition systems were trained with the same hyperparameters as
described above. For a fairer comparison, a common, general language model was
used for all the tests. Hence the higher WER for the Parliament corpus tested on
itself than the reported 8.40\%.

@@

I have presented a new corpus of spoken Czech suitable for training speech
recognition systems based on data in the public domain. The corpus size exceeds
by an order the size of other freely available such corpora. A speech
recognition system with competitive performance was made to show the fitness
of the dataset to the purpose.

Among the compared corpora, the Czech parliament corpus performs by far best
even in speech recognition outside its domain.

### 2020-05-04 2020-tsd-brno-svolocz/svolocz.tex
svolocz: add cross-corpora ASR

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{rotating}

\usepackage{url}
\urldef{\mailsa}\path|kruza@ufal.mff.cuni.cz|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Czech parliament meeting recordings as ASR training data}

% a short form should be given in case it is too long for the running head
\titlerunning{Czech parliament meeting recordings as ASR training data}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jan Oldřich Krůza}
%
\authorrunning{Jan Oldřich Krůza}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University
\mailsa\\
\url{ufal.mff.cuni.cz}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Czech parliament meeting recordings as ASR training data}
\tocauthor{Jan Oldřich Krůza}
\maketitle

\begin{abstract}
I present a way to leverage the stenographed recordings of the Czech parliament
meetings for purposes of training a speech-to-text system. The article presents
a method for scraping the data, acquiring word-level alignment and selecting
reliable parts of the imprecise transcript. Finally, I present an ASR system
trained on these data.
\keywords{speech corpus, speech recognition, czech}
\end{abstract}

\section{Introduction}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Czech parliament meeting recordings as ASR training data}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Oldřich Krůza\inst{1}\orcidID{0000-0002-7510-6470}}
%
\authorrunning{Jan Krůza}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
\email{kruza@ufal.mff.cuni.cz}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
I present a way to leverage the stenographed recordings of the Czech parliament
meetings for purposes of training a speech-to-text system. The article presents
a method for scraping the data, acquiring word-level alignment and selecting
reliable parts of the imprecise transcript. Finally, I present an ASR system
trained on these data.
\keywords{speech corpus, speech recognition, czech}
\end{abstract}

\section{Introduction}
\label{sec:intro}
